Subgraph Isomorphism With Side Constraints

### 2020-11-17 paper.tex
More plottery

\usepackage{listings}
\lstset{
basicstyle=\small\ttfamily,
mathescape,
escapeinside={(*}{*)},
numbers=none,
keywordstyle=\bfseries,  %\color{red}
keywords = {language, Essence, given, letting, find, such, that,
            bool, int, matrix, enum, variant, record, set, mset,
            sequence, function, relation, partition, 
            domain, total, surjective, be,
            forAll, exists, sum, injective, in, preImage, range,
            new, type, intersect, union, from,
            minimising, maximising, of, indexed, by, and,
            defined, maxSize, maxNumParts, size, regular, language, cheese
            }
showstringspaces=false,
tabsize=1,
breaklines=true,
breakatwhitespace=false,
}

% \usepackage{showframe}

@@

\begin{figure}[p]
    \includegraphics{gen-graph-nosideconstraints.pdf}\hfill\includegraphics{gen-graph-oddeven.pdf}
    \medskip
    \includegraphics{gen-graph-mostlyodd.pdf}\hfill\includegraphics{gen-graph-parity.pdf}
    \caption{Comparing different approaches to hybrid solving. On the top row, ``no side
    constraints'' then with the ``more odd target vertices than even target vertices'' side
    constraint; on the bottom row, the ``mostly odd target vertices'' side constraint on the left,
    and the ``odd to odd, even to even'' side constraint on the right.}\label{figure:cumulative}
\end{figure}

>>>>

\usepackage{listings}
\lstset{
basicstyle=\small\ttfamily,
mathescape,
escapeinside={(*}{*)},
numbers=none,
keywordstyle=\bfseries\color{blue},
keywords = {language, Essence, given, letting, find, such, that,
            bool, int, matrix, enum, variant, record, set, mset,
            sequence, function, relation, partition, 
            domain, total, surjective, be,
            forAll, exists, sum, injective, in, preImage, range,
            new, type, intersect, union, from,
            minimising, maximising, of, indexed, by, and,
            defined, maxSize, maxNumParts, size, regular, language, cheese
            }
showstringspaces=false,
tabsize=1,
breaklines=true,
breakatwhitespace=false,
}

\usepackage{showframe}

@@

\begin{figure}[p]
    \includegraphics{gen-graph-nosideconstraints.pdf}\hfill\includegraphics{gen-graph-oddeven.pdf}
    \bigskip
    \includegraphics{gen-graph-mostlyodd.pdf}\hfill\includegraphics{gen-graph-parity.pdf}
    \caption{Comparing different approaches to hybrid solving. On the top row, ``no side
    constraints'' then with the ``more odd target vertices than even target vertices'' side
    constraint; on the bottom row, the ``mostly odd target vertices'' side constraint on the left,
    and the ``odd to odd, even to even'' side constraint on the right.}\label{figure:cumulative}
\end{figure}
